### 2024-03-18 sections/3algebras.tex
Added comment on physical interpretation.

>>>>

\begin{remark}
    As noted at the beginning of \ss 2, the physical interpretation of this version of factorization homology is a way to take a spacetime $M$ and its local observables $A$, and construct \emph{some}, and typically not all, of the global observables. The previous \Cref{thm:disk_alg=lcfa} and \Cref{cor:disk_alg=falg} transfer this observation to factorization algebras, which aligns with the observation of \cite{cg2016} that the current version of factorization algebras can only deal with perturbative quantum field theory. 
\end{remark}
